PANCHANGE_analysis

### 2020-12-09 PANCHANGE_analysis.Rmd
added chunk to source all function scripts in FunctionLib folder

@@

## Forest plots
### disorder
```{r forest plot by disorder prepan, fig.height=14, fig.width=8}

@@

```{r forest plot by disorder retro, fig.height=14, fig.width=8}

@@

### disorder (no PCL)
```{r forest plot by disorder prepan, fig.height=14, fig.width=8}

@@

```{r forest plot by disorder retro, fig.height=14, fig.width=8}

@@

### time point 
```{r forest plot by time point gad, fig.height=14, fig.width=8}

@@

```{r forest plot by time point phq, fig.height=14, fig.width=8}

@@

```{r forest plot by sample retro only gad, fig.height=14, fig.width=8}

@@

```{r forest plot by sample retro only phq, fig.height=14, fig.width=8}

@@

```{r forest plot by sample retro only pcl, fig.height=14, fig.width=8}

>>>>

```{r call in function library functions}

# source all functions in the function library folder

files.sources = list.files("FunctionLib/")
sapply(files.sources, source)

@@

## Forest plots
### disorder
```{r forest plot by disorder prepan, fig.height=20, fig.width=12}

@@

```{r forest plot by disorder retro, fig.height=20, fig.width=12}

@@

### disorder (no PCL)
```{r forest plot by disorder prepan no pcl, fig.height=20, fig.width=12}

@@

```{r forest plot by disorder retro no pcl, fig.height=20, fig.width=12}

@@

### time point 
```{r forest plot by time point gad, fig.height=20, fig.width=12}

@@

```{r forest plot by time point phq, fig.height=20, fig.width=12}

@@

```{r forest plot by sample retro only gad, fig.height=20, fig.width=12}

@@

```{r forest plot by sample retro only phq, fig.height=20, fig.width=12}

@@

```{r forest plot by sample retro only pcl, fig.height=20, fig.width=12}
